---
title: "Concrete Plot"
author: "Javier Angoy"
date: "November 14, 2017"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Overview
Concrete is the most important material in civil engineering. The concrete compressive strength is a highly nonlinear function of age and ingredients.
	
This document contains a plot for the [concrete](http://archive.ics.uci.edu/ml/datasets/Concrete+Compressive+Strength) data set. An overview for the data:
```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(plotly)
library(ggplot2)
library(AppliedPredictiveModeling)
data(concrete)
str(concrete)
```

### Our Variables:

>- Cement (component 1) -- quantitative -- kg in a m3 mixture
>- Water (component 4) -- quantitative -- kg in a m3 mixture 
>- Age -- quantitative -- Day (1~365)
>- Concrete compressive strength -- quantitative -- MPa

## Concrete Plot

```{r, echo=FALSE, message=FALSE, warning=FALSE}
dd <- transform(concrete, Age = ts(Age))

df <- dd[order(factor(dd$Age)),]

p <- ggplot(df, aes(Cement,CompressiveStrength)) +
    geom_point(aes(frame = Age, colour=Water), size=6) + 
    scale_colour_gradient(low = "white", high = "black") +
    stat_smooth() 

ggplotly(p, width = 1000, height = 800)  %>% 
    
layout(title = 'Cement versus Compressive Strenght Plot by Age (days). Colour: Water',
       autosize = T, showlegend = T ) %>% 
    animation_slider(currentvalue = list(prefix = "Age (days): ", font = list(color="red")))
```

